Graphs for 1000  Generations

### 2021-07-13 graphs_newt_snakes/fig_1000.Rmd
Just added the 12 starting point figures. Some of them look really cool. Need to think more about what they mean. Also made a html file

# Makeing of the Figure
Loop through the files and find the max and min of each of the species phenotypes
Then set up a graph with the average phenotype

This section of code loops though the files and finds the maximum and minumum pheotypes of newts and snakes. and make two lines (red for newts blue for snakes) and keep a minimum about of info in mem at a time

@@

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  file <- file[complete.cases(file), ]
  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
  file$mean_dif[file$mean_dif == 0] <- 0.01
  file$pos <- "Snake"
  file$pos[file$mean_dif < 0] <- "Newt"
  file$pos[file$mean_dif ==  0.01] <- "Equal"

@@

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
  file <- file[complete.cases(file), ]
 p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color = darken("darkred")) +
   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color = darken("steelblue")) +
  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color = lighten("steelblue"))
 i = i+1
}
return(p)
}

@@

@@

This figure represents the difference between the snake and the newt phenotype. The pink lines indicate that the newt is more toxit than the snakes, while the blue line indicates that the snakes are more resitant than the newts

@@

For this figure I want there to be 2 sets of points (4 complete points) for each simulation taking the first and last mean phenotype for the newt and the snake. Essentially, asking if the phenotypes of the newts and snakes changed over 1000 generations?

@@

@@

# The Correct Experiment

@@

Again I looped through the files and find the max and min of each of the species pheotypes
Then set up a graph with the average pheotypes over 1000 generations (red line for newts blue linesfor snakes).

@@

```{r data 1 msprime photype graph, echo=FALSE}
files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

@@

```{r data 1 msprime dif pheno graph, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
title = "1sim: Phenotype Measurements for Newts and Snake"
q = phenotype_graph(files, my_mean, my_sd, title, is_log = TRUE)
p = phenotype_graph(files, my_mean, my_sd, title)
q
p 
```

@@

```{r data from multiple msprime, echo=FALSE}

@@

# Expanded Experiment 2sims: 
This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked. I ran 144 SLiM simulations & MSprime with different parameters values.

@@

```
some of these values are in quotes, why?

@@

p 
```
## How much did the phenotypes of newts and snakes change over 1000 generations

@@

#p
#q

@@

>>>>

# The Functions

I made functions to collect data and make figures for all of the simulations that I run. The data generator will take a list of files and find things like max, min, mean and sd. The functions that creates the figures will usually take a list of files, a mean, sd and title. These functions will loop through the list of files and return the specific figure. On some there is also the option to log the y axis.

@@

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  file <- file[complete.cases(file), ]
  file$mean_dif = as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno)
  file$mean_dif[file$mean_dif == 0] <- 0.01
  file$pos <- "Snake"
  file$pos[file$mean_dif < 0] <- "Newt"
  file$pos[file$mean_dif ==  0.01] <- "ZEqual"

@@

  file <- read.table(current_file, header = TRUE)
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- 0
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- 0
  file <- file[complete.cases(file), ]
 p <- p + geom_point(data= file, x = i, aes(y = as.numeric(Newt_mean_Pheno[1])+0.1), color = darken("darkred")) +
   geom_point(data= file,x = i, aes(y = as.numeric(Newt_mean_Pheno[50])+0.1), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[1])+0.1), color = darken("steelblue")) +
  geom_point(data= file, x = i, aes(y = as.numeric(Snake_mean_Pheno[50])+0.1), color = lighten("steelblue"))+
  geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Newt_mean_Pheno[1])+0.1, yend=as.numeric(Newt_mean_Pheno[50])+0.1), size = 0.3, arrow = arrow(length = unit(0.5, "cm")), color="darkred")+
   geom_segment(data = file, x=i, xend=i, aes( y=as.numeric(Snake_mean_Pheno[1])+0.1, yend=as.numeric(Snake_mean_Pheno[50])+0.1), size = 0.3, arrow = arrow(length = unit(0.5, "cm")), color="steelblue")

 i = i+1
}
return(p)
}

@@

# Data Collection and Making of the Figure

Loop through the files and find the max and min of each of the species phenotypes
Then set up a graph with the average phenotype:

@@

## Difference Between Snake and Newt Pheotypes

This figure represents the difference between the snake and the newt phenotype. The pink lines indicate that the newt is more toxic than the snakes, while the blue line indicates that the snakes are more resistant than the newts. Sometime there are neutral cases and the colors get mixed, but i have plans to fix this and make the figure better overall (7/13/2021).

@@

For this figure I want there to be 2 sets of points (4 complete points) for each simulation taking the first and last mean phenotype for the newt and the snake. Essentially, asking if the phenotypes of the newts and snakes changed over 1000 generations? I changed these points into arrows to show the direction of phenotype change.

@@

## Trasforming the Phenotypes Back

@@

# The Correct Experiment (Known as 1 Sim)

@@

Again I looped through the files and find the max and min of each of the species pheotypes
Then set up a graph with the average pheotypes over 1000 generations (red line for newts blue lines for snakes).

@@

```{r data 1 msprime data, echo=FALSE}
files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

@@

```{r data 1 msprime pheno graph, echo=FALSE}

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
title = "1sim: Phenotype Measurements for Newts and Snake"
p = phenotype_graph(files, my_mean, my_sd, title)
p 
```

@@

```{r 1sim differences, echo=FALSE}

@@

# Expanded Experiment 2sims:

This time I examine what the SLIM script would generate is both the MSprime and SLIM are ran with the variables that I picked. I ran 143 SLiM simulations & MSprime with different parameters values.

@@

@@

@@

@@

```{r 12 points data collection, echo=FALSE}

print("------------------------------------------------------------")
print("                         TRIAL 1                            ")
print("------------------------------------------------------------")

files_1 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_1_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_1)

newt_max_pheno_1_1 = out[1]
snake_max_pheno_1_1 = out[2]
newt_min_pheno_1_1  = out[3]
snake_min_pheno_1_1 = out[4]
true_max_1_1 = out[5]
true_min_1_1 = out[6]
min_difference_1_1 = out[7]
max_difference_1_1 = out[8]
my_mean_1 = out[9]
my_sd_1 = out[10]
mean_mean_dif_1 = out[11]
sd_mean_dif_1 = out[12]

print(paste0("Newt max pheno trial 1: ", newt_max_pheno_1_1))
print(paste0("Snake max phenot trial 1: ", snake_max_pheno_1_1))
print(paste0("Newt min pheno trial 1: ", newt_min_pheno_1_1))
print(paste0("Snake min Pheno trial 1: ", snake_min_pheno_1_1))
print(paste0("Mean of combined snake and newt trial 1: ", my_mean_1))
print(paste0("Sd of combined snake and newt trial 1: ", my_sd_1))
print(paste0("Mean of the mean difference trial 1: ", mean_mean_dif_1))
print(paste0("SD of the mean difference trial 1: ", sd_mean_dif_1))

print("------------------------------------------------------------")
print("                         TRIAL 2                            ")
print("------------------------------------------------------------")

files_2 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_2_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_2)

newt_max_pheno_1_2 = out[1]
snake_max_pheno_1_2 = out[2]
newt_min_pheno_1_2  = out[3]
snake_min_pheno_1_2 = out[4]
true_max_1_2 = out[5]
true_min_1_2 = out[6]
min_difference_1_2 = out[7]
max_difference_1_2 = out[8]
my_mean_2 = out[9]
my_sd_2 = out[10]
mean_mean_dif_2 = out[11]
sd_mean_dif_2 = out[12]

print(paste0("Newt max pheno trial 2: ", newt_max_pheno_1_2))
print(paste0("Snake max phenot trial 2: ", snake_max_pheno_1_2))
print(paste0("Newt min pheno trial 2: ", newt_min_pheno_1_2))
print(paste0("Snake min Pheno trial 2: ", snake_min_pheno_1_2))
print(paste0("Mean of combined snake and newt trial 2: ", my_mean_2))
print(paste0("Sd of combined snake and newt trial 2: ", my_sd_2))
print(paste0("Mean of the mean difference trial 2: ", mean_mean_dif_2))
print(paste0("SD of the mean difference trial 2: ", sd_mean_dif_2))

print("------------------------------------------------------------")
print("                         TRIAL 3                            ")
print("------------------------------------------------------------")

files_3 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_3_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_3)

newt_max_pheno_1_3 = out[1]
snake_max_pheno_1_3 = out[2]
newt_min_pheno_1_3  = out[3]
snake_min_pheno_1_3 = out[4]
true_max_1_3 = out[5]
true_min_1_3 = out[6]
min_difference_1_3 = out[7]
max_difference_1_3 = out[8]
my_mean_3 = out[9]
my_sd_3 = out[10]
mean_mean_dif_3 = out[11]
sd_mean_dif_3 = out[12]

print(paste0("Newt max pheno trial 3: ", newt_max_pheno_1_3))
print(paste0("Snake max phenot trial 3: ", snake_max_pheno_1_3))
print(paste0("Newt min pheno trial 3: ", newt_min_pheno_1_3))
print(paste0("Snake min Pheno trial 3: ", snake_min_pheno_1_3))
print(paste0("Mean of combined snake and newt trial 3: ", my_mean_3))
print(paste0("Sd of combined snake and newt trial 3: ", my_sd_3))
print(paste0("Mean of the mean difference trial 3: ", mean_mean_dif_3))
print(paste0("SD of the mean difference trial 3: ", sd_mean_dif_3))

print("------------------------------------------------------------")
print("                         TRIAL 4                            ")
print("------------------------------------------------------------")

files_4 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_4_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_4)

newt_max_pheno_1_4 = out[1]
snake_max_pheno_1_4 = out[2]
newt_min_pheno_1_4  = out[3]
snake_min_pheno_1_4 = out[4]
true_max_1_4 = out[5]
true_min_1_4 = out[6]
min_difference_1_4 = out[7]
max_difference_1_4 = out[8]
my_mean_4 = out[9]
my_sd_4 = out[10]
mean_mean_dif_4 = out[11]
sd_mean_dif_4 = out[12]

print(paste0("Newt max pheno trial 4: ", newt_max_pheno_1_4))
print(paste0("Snake max phenot trial 4: ", snake_max_pheno_1_4))
print(paste0("Newt min pheno trial 4: ", newt_min_pheno_1_4))
print(paste0("Snake min Pheno trial 4: ", snake_min_pheno_1_4))
print(paste0("Mean of combined snake and newt trial 4: ", my_mean_4))
print(paste0("Sd of combined snake and newt trial 4: ", my_sd_4))
print(paste0("Mean of the mean difference trial 4: ", mean_mean_dif_4))
print(paste0("SD of the mean difference trial 4: ", sd_mean_dif_4))

print("------------------------------------------------------------")
print("                         TRIAL 5                            ")
print("------------------------------------------------------------")

files_5 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_5_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_5)

newt_max_pheno_1_5 = out[1]
snake_max_pheno_1_5 = out[2]
newt_min_pheno_1_5  = out[3]
snake_min_pheno_1_5 = out[4]
true_max_1_5 = out[5]
true_min_1_5 = out[6]
min_difference_1_5 = out[7]
max_difference_1_5 = out[8]
my_mean_5 = out[9]
my_sd_5 = out[10]
mean_mean_dif_5 = out[11]
sd_mean_dif_5 = out[12]

print(paste0("Newt max pheno trial 5: ", newt_max_pheno_1_5))
print(paste0("Snake max phenot trial 5: ", snake_max_pheno_1_5))
print(paste0("Newt min pheno trial 5: ", newt_min_pheno_1_5))
print(paste0("Snake min Pheno trial 5: ", snake_min_pheno_1_5))
print(paste0("Mean of combined snake and newt trial 5: ", my_mean_5))
print(paste0("Sd of combined snake and newt trial 5: ", my_sd_5))
print(paste0("Mean of the mean difference trial 5: ", mean_mean_dif_5))
print(paste0("SD of the mean difference trial 5: ", sd_mean_dif_5))

print("------------------------------------------------------------")
print("                         TRIAL 6                            ")
print("------------------------------------------------------------")

files_6 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_6_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_6)

newt_max_pheno_1_6 = out[1]
snake_max_pheno_1_6 = out[2]
newt_min_pheno_1_6  = out[3]
snake_min_pheno_1_6 = out[4]
true_max_1_6 = out[5]
true_min_1_6 = out[6]
min_difference_1_6 = out[7]
max_difference_1_6 = out[8]
my_mean_6 = out[9]
my_sd_6 = out[10]
mean_mean_dif_6 = out[11]
sd_mean_dif_6 = out[12]

print(paste0("Newt max pheno trial 6: ", newt_max_pheno_1_6))
print(paste0("Snake max pheno trial 6: ", snake_max_pheno_1_6))
print(paste0("Newt min pheno trial 6: ", newt_min_pheno_1_6))
print(paste0("Snake min Pheno  trial 6: ", snake_min_pheno_1_6))
print(paste0("Mean of combined snake and newt trial 6: ", my_mean_6))
print(paste0("Sd of combined snake and newt trial 6: ", my_sd_6))
print(paste0("Mean of the mean difference trial 6: ", mean_mean_dif_6))
print(paste0("SD of the mean difference trial 6: ", sd_mean_dif_6))

print("------------------------------------------------------------")
print("                         TRIAL 7                            ")
print("------------------------------------------------------------")

files_7 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_7_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_7)

newt_max_pheno_1_7 = out[1]
snake_max_pheno_1_7 = out[2]
newt_min_pheno_1_7  = out[3]
snake_min_pheno_1_7 = out[4]
true_max_1_7 = out[5]
true_min_1_7 = out[6]
min_difference_1_7 = out[7]
max_difference_1_7 = out[8]
my_mean_7 = out[9]
my_sd_7 = out[10]
mean_mean_dif_7 = out[11]
sd_mean_dif_7 = out[12]

print(paste0("Newt max pheno trial 7: ", newt_max_pheno_1_7))
print(paste0("Snake max phenot trial 7: ", snake_max_pheno_1_7))
print(paste0("Newt min pheno trial 7: ", newt_min_pheno_1_7))
print(paste0("Snake min Pheno trial 7: ", snake_min_pheno_1_7))
print(paste0("Mean of combined snake and newt trial 7: ", my_mean_7))
print(paste0("Sd of combined snake and newt trial 7: ", my_sd_7))
print(paste0("Mean of the mean difference trial 7: ", mean_mean_dif_7))
print(paste0("SD of the mean difference trial 7: ", sd_mean_dif_7))

print("------------------------------------------------------------")
print("                         TRIAL 8                            ")
print("------------------------------------------------------------")

files_8 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_8_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_8)

newt_max_pheno_1_8 = out[1]
snake_max_pheno_1_8 = out[2]
newt_min_pheno_1_8  = out[3]
snake_min_pheno_1_8 = out[4]
true_max_1_8 = out[5]
true_min_1_8 = out[6]
min_difference_1_8 = out[7]
max_difference_1_8 = out[8]
my_mean_8 = out[9]
my_sd_8 = out[10]
mean_mean_dif_8 = out[11]
sd_mean_dif_8 = out[12]

print(paste0("Newt max pheno trial 8: ", newt_max_pheno_1_8))
print(paste0("Snake max phenot trial 8: ", snake_max_pheno_1_8))
print(paste0("Newt min pheno trial 8: ", newt_min_pheno_1_8))
print(paste0("Snake min Pheno trial 8: ", snake_min_pheno_1_8))
print(paste0("Mean of combined snake and newt trial 8: ", my_mean_8))
print(paste0("Sd of combined snake and newt trial 8: ", my_sd_8))
print(paste0("Mean of the mean difference trial 8: ", mean_mean_dif_8))
print(paste0("SD of the mean difference trial 8: ", sd_mean_dif_8))

print("------------------------------------------------------------")
print("                         TRIAL 9                            ")
print("------------------------------------------------------------")

files_9 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_9", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_9)

newt_max_pheno_1_9 = out[1]
snake_max_pheno_1_9 = out[2]
newt_min_pheno_1_9  = out[3]
snake_min_pheno_1_9 = out[4]
true_max_1_9 = out[5]
true_min_1_9 = out[6]
min_difference_1_9 = out[7]
max_difference_1_9 = out[8]
my_mean_9 = out[9]
my_sd_9 = out[10]
mean_mean_dif_9 = out[11]
sd_mean_dif_9 = out[12]

print(paste0("Newt max pheno trial 9: ", newt_max_pheno_1_9))
print(paste0("Snake max phenot trial 9: ", snake_max_pheno_1_9))
print(paste0("Newt min pheno trial 9: ", newt_min_pheno_1_9))
print(paste0("Snake min Pheno trial 9: ", snake_min_pheno_1_9))
print(paste0("Mean of combined snake and newt trial 9: ", my_mean_9))
print(paste0("Sd of combined snake and newt trial 9: ", my_sd_9))
print(paste0("Mean of the mean difference trial 9: ", mean_mean_dif_9))
print(paste0("SD of the mean difference trial 9: ", sd_mean_dif_9))

print("------------------------------------------------------------")
print("                         TRIAL 10                           ")
print("------------------------------------------------------------")

files_10 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_10_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_10)

newt_max_pheno_1_10 = out[1]
snake_max_pheno_1_10 = out[2]
newt_min_pheno_1_10  = out[3]
snake_min_pheno_1_10 = out[4]
true_max_1_10 = out[5]
true_min_1_10 = out[6]
min_difference_1_10 = out[7]
max_difference_1_10 = out[8]
my_mean_10 = out[9]
my_sd_10 = out[10]
mean_mean_dif_10 = out[11]
sd_mean_dif_10 = out[12]

print(paste0("Newt max pheno trial 10: ", newt_max_pheno_1_10))
print(paste0("Snake max phenot trial 10: ", snake_max_pheno_1_10))
print(paste0("Newt min pheno trial 10: ", newt_min_pheno_1_10))
print(paste0("Snake min Pheno trial 10: ", snake_min_pheno_1_10))
print(paste0("Mean of combined snake and newt trial 10: ", my_mean_10))
print(paste0("Sd of combined snake and newt trial 10: ", my_sd_10))
print(paste0("Mean of the mean difference trial 10: ", mean_mean_dif_10))
print(paste0("SD of the mean difference trial 10: ", sd_mean_dif_10))

print("------------------------------------------------------------")
print("                         TRIAL 11                          ")
print("------------------------------------------------------------")

files_11 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_11_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_11)

newt_max_pheno_1_11 = out[1]
snake_max_pheno_1_11 = out[2]
newt_min_pheno_1_11  = out[3]
snake_min_pheno_1_11 = out[4]
true_max_1_11 = out[5]
true_min_1_11 = out[6]
min_difference_1_11 = out[7]
max_difference_1_11 = out[8]
my_mean_11 = out[9]
my_sd_11 = out[10]
mean_mean_dif_11 = out[11]
sd_mean_dif_11 = out[12]

print(paste0("Newt max pheno trial 11: ", newt_max_pheno_1_11))
print(paste0("Snake max phenot trial 11: ", snake_max_pheno_1_11))
print(paste0("Newt min pheno trial 11: ", newt_min_pheno_1_11))
print(paste0("Snake min Pheno trial 11: ", snake_min_pheno_1_11))
print(paste0("Mean of combined snake and newt trial 11: ", my_mean_11))
print(paste0("Sd of combined snake and newt trial 11: ", my_sd_11))
print(paste0("Mean of the mean difference trial 11: ", mean_mean_dif_11))
print(paste0("SD of the mean difference trial 11: ", sd_mean_dif_11))

print("------------------------------------------------------------")
print("                         TRIAL 12                           ")
print("------------------------------------------------------------")

files_12 <- list.files(path="~/Desktop/text_files_12", pattern="file_small_trial_12_", full.names=TRUE, recursive=FALSE)

out = collect_data_points(files_12)

newt_max_pheno_1_12 = out[1]
snake_max_pheno_1_12 = out[2]
newt_min_pheno_1_12  = out[3]
snake_min_pheno_1_12 = out[4]
true_max_1_12 = out[5]
true_min_1_12 = out[6]
min_difference_1_12 = out[7]
max_difference_1_12 = out[8]
my_mean_12 = out[9]
my_sd_12 = out[10]
mean_mean_dif_12 = out[11]
sd_mean_dif_12 = out[12]

print(paste0("Newt max pheno trial 12: ", newt_max_pheno_1_12))
print(paste0("Snake max pheno trial 12: ", snake_max_pheno_1_12))
print(paste0("Newt min pheno trial 12: ", newt_min_pheno_1_12))
print(paste0("Snake min Pheno trial 12: ", snake_min_pheno_1_12))
print(paste0("Mean of combined snake and newt trial 12: ", my_mean_12))
print(paste0("Sd of combined snake and newt trial 12: ", my_sd_12))
print(paste0("Mean of the mean difference trial 12: ", mean_mean_dif_12))
print(paste0("SD of the mean difference trial 12: ", sd_mean_dif_12))

```{r phenotype graph 12 points, echo=FALSE}

title = "Trial 1 Phenotype Measurements for Newts and Snake"
p_1 = phenotype_graph(files_1, my_mean_1, my_sd_1, title)
#p_1

title = "Trial 2 Phenotype Measurements for Newts and Snake"
p_2 = phenotype_graph(files_2, my_mean_2, my_sd_2, title)
#p_2

title = "Trial 3 Phenotype Measurements for Newts and Snake Trial 3"
p_3 = phenotype_graph(files_3, my_mean_3, my_sd_3, title)
#p_3

title = "Trial 4 Phenotype Measurements for Newts and Snake"
p_4 = phenotype_graph(files_4, my_mean_4, my_sd_4, title)
#p_4

grid.arrange(p_1, p_2, p_3, p_4, nrow = 2)

title = "Trial 5 Phenotype Measurements for Newts and Snake"
p_5 = phenotype_graph(files_5, my_mean_5, my_sd_5, title)
#p_5

title = "Trial 6 Phenotype Measurements for Newts and Snake"
p_6 = phenotype_graph(files_6, my_mean_6, my_sd_6, title)
#p_6

title = "Trial 7 Phenotype Measurements for Newts and Snake"
p_7 = phenotype_graph(files_7, my_mean_7, my_sd_7, title)
#p_7

title = "Trial 8 Phenotype Measurements for Newts and Snake"
p_8 = phenotype_graph(files_8, my_mean_8, my_sd_8, title)
#p_8

grid.arrange(p_5, p_6, p_7, p_8, nrow=2)

title = "Trial 9 Phenotype Measurements for Newts and Snake"
p_9 = phenotype_graph(files_9, my_mean_9, my_sd_9, title)
#p_9

title = "Trial 10 Phenotype Measurements for Newts and Snake"
p_10 = phenotype_graph(files_10, my_mean_10, my_sd_10, title)
#p_10

title = "Trial 11 Phenotype Measurements for Newts and Snake"
p_11 = phenotype_graph(files_11, my_mean_11, my_sd_11, title)
#p_11

title = "Trial 12  Phenotype Measurements for Newts and Snake"
p_12 = phenotype_graph(files_12, my_mean_12, my_sd_12, title)
#p_12

grid.arrange(p_9, p_10, p_11, p_12, nrow=2)

```{r 12 sim pheno dif, echo=FALSE}

title = "Trial 1: Difference Between Phenotypes (Snakes-Newts)"
d_1 = differnce_graph(files_1, mean_mean_dif_1, sd_mean_dif_1, min_difference_1_1, max_difference_1_1, title)

title = "Trial 2: Difference Between Phenotypes (Snakes-Newts)"
d_2 = differnce_graph(files_2, mean_mean_dif_2, sd_mean_dif_2, min_difference_1_2, max_difference_1_2, title)

title = "Trial 3: Difference Between Phenotypes (Snakes-Newts)"
d_3 = differnce_graph(files_3, mean_mean_dif_3, sd_mean_dif_3, min_difference_1_3, max_difference_1_3, title)

title = "Trial 4: Difference Between Phenotypes (Snakes-Newts)"
d_4 = differnce_graph(files_4, mean_mean_dif_4, sd_mean_dif_4, min_difference_1_4, max_difference_1_4, title)

grid.arrange(d_1, d_2, d_3, d_4, nrow = 2)

title = "Trial 5: Difference Between Phenotypes (Snakes-Newts)"
d_5 = differnce_graph(files_5, mean_mean_dif_5, sd_mean_dif_5, min_difference_1_5, max_difference_1_5, title)

title = "Trial 6: Difference Between Phenotypes (Snakes-Newts)"
d_6 = differnce_graph(files_6, mean_mean_dif_6, sd_mean_dif_6, min_difference_1_6, max_difference_1_6, title)

title = "Trial 7: Difference Between Phenotypes (Snakes-Newts)"
d_7 = differnce_graph(files_7, mean_mean_dif_7, sd_mean_dif_7, min_difference_1_7, max_difference_1_7, title)

title = "Trial 8: Difference Between Phenotypes (Snakes-Newts)"
d_8 = differnce_graph(files_8, mean_mean_dif_8, sd_mean_dif_8, min_difference_1_8, max_difference_1_8, title)

grid.arrange(d_5, d_6, d_7, d_8, nrow = 2)

title = "Trial 9: Difference Between Phenotypes (Snakes-Newts)"
d_9 = differnce_graph(files_9, mean_mean_dif_9, sd_mean_dif_9, min_difference_1_9, max_difference_1_9, title)

title = "Trial 10: Difference Between Phenotypes (Snakes-Newts)"
d_10 = differnce_graph(files_10, mean_mean_dif_10, sd_mean_dif_10, min_difference_1_10, max_difference_1_10, title)

title = "Trial 11: Difference Between Phenotypes (Snakes-Newts)"
d_11 = differnce_graph(files_11, mean_mean_dif_11, sd_mean_dif_11, min_difference_1_11, max_difference_1_11, title)

title = "Trial 12: Difference Between Phenotypes (Snakes-Newts)"
d_12 = differnce_graph(files_12, mean_mean_dif_12, sd_mean_dif_12, min_difference_1_12, max_difference_1_12, title)

grid.arrange(d_9, d_10, d_11, d_12, nrow = 2)

```{r 12 sim pheno change, echo=FALSE}

title = "Trial 1 12sim: Phenotype Change"
c_1=phenotype_change_graph(files_1, my_mean_1, my_sd_1, title)

title = "Trial 2 12sim: Phenotype Change"
c_2=phenotype_change_graph(files_2, my_mean_2, my_sd_2, title)

title = "Trial 3 12sim: Phenotype Change"
c_3=phenotype_change_graph(files_3, my_mean_3, my_sd_3, title)

title = "Trial 4 12sim: Phenotype Change"
c_4=phenotype_change_graph(files_4, my_mean_4, my_sd_4, title)

grid.arrange(c_1, c_2, c_3, c_4, nrow = 2)

title = "Trial 5 12sim: Phenotype Change"
c_5=phenotype_change_graph(files_5, my_mean_5, my_sd_5, title)

title = "Trial 6 12sim: Phenotype Change"
c_6=phenotype_change_graph(files_6, my_mean_6, my_sd_6, title)

title = "Trial 7 12sim: Phenotype Change"
c_7=phenotype_change_graph(files_7, my_mean_7, my_sd_7, title)

title = "Trial 8 12sim: Phenotype Change"
c_8=phenotype_change_graph(files_8, my_mean_8, my_sd_8, title)

grid.arrange(c_5, c_6, c_7, c_8, nrow = 2)

title = "Trial 9 12sim: Phenotype Change"
c_9=phenotype_change_graph(files_9, my_mean_9, my_sd_9, title)

title = "Trial 10 12sim: Phenotype Change"
c_10=phenotype_change_graph(files_10, my_mean_10, my_sd_10, title)

title = "Trial 11 12sim: Phenotype Change"
c_11=phenotype_change_graph(files_11, my_mean_11, my_sd_11, title)

title = "Trial 12 12sim: Phenotype Change"
c_12=phenotype_change_graph(files_12, my_mean_12, my_sd_12, title)

grid.arrange(c_9, c_10, c_11, c_12, nrow = 2)

```{r 12 point trasformation , echo=FALSE}

title1 = "Trial 1: Newt trasnformed vs un-trasformed"
title2 = "Trial 1: Snake trasnformed vs un-trasformed"
graph_1 = untrasform(files_1, my_mean_1, my_sd_1, title1, title2, is_log=FALSE)

title1 = "Trial 2: Newt trasnformed vs un-trasformed"
title2 = "Trial 2: Snake trasnformed vs un-trasformed"
graph_2 = untrasform(files_2, my_mean_2, my_sd_2, title1, title2, is_log=FALSE)

title1 = "Trial 3: Newt trasnformed vs un-trasformed"
title2 = "Trial 3: Snake trasnformed vs un-trasformed"
graph_3 = untrasform(files_3, my_mean_3, my_sd_3, title1, title2, is_log=FALSE)

title1 = "Trial 4: Newt trasnformed vs un-trasformed"
title2 = "Trial 4: Snake trasnformed vs un-trasformed"
graph_4 = untrasform(files_4, my_mean_4, my_sd_4, title1, title2, is_log=FALSE)

grid.arrange(graph_1[[1]], graph_1[[2]], graph_2[[1]], graph_2[[2]], graph_3[[1]], graph_3[[2]], graph_4[[1]], graph_4[[2]], nrow = 4)

title1 = "Trial 5: Newt trasnformed vs un-trasformed"
title2 = "Trial 5: Snake trasnformed vs un-trasformed"
graph_5 = untrasform(files_5, my_mean_5, my_sd_5, title1, title2, is_log=FALSE)

title1 = "Trial 6: Newt trasnformed vs un-trasformed"
title2 = "Trial 6: Snake trasnformed vs un-trasformed"
graph_6 = untrasform(files_6, my_mean_6, my_sd_6, title1, title2, is_log=FALSE)

title1 = "Trial 7: Newt trasnformed vs un-trasformed"
title2 = "Trial 7: Snake trasnformed vs un-trasformed"
graph_7 = untrasform(files_7, my_mean_7, my_sd_7, title1, title2, is_log=FALSE)

title1 = "Trial 8: Newt trasnformed vs un-trasformed"
title2 = "Trial 8: Snake trasnformed vs un-trasformed"
graph_8 = untrasform(files_8, my_mean_8, my_sd_8, title1, title2, is_log=FALSE)

grid.arrange(graph_5[[1]], graph_5[[2]], graph_6[[1]], graph_6[[2]], graph_7[[1]], graph_7[[2]], graph_8[[1]], graph_8[[2]], nrow = 4)

title1 = "Trial 9: Newt trasnformed vs un-trasformed"
title2 = "Trial 9: Snake trasnformed vs un-trasformed"
graph_9 = untrasform(files_9, my_mean_9, my_sd_9, title1, title2, is_log=FALSE)

title1 = "Trial 10: Newt trasnformed vs un-trasformed"
title2 = "Trial 10: Snake trasnformed vs un-trasformed"
graph_10 = untrasform(files_10, my_mean_10, my_sd_10, title1, title2, is_log=FALSE)

title1 = "Trial 11: Newt trasnformed vs un-trasformed"
title2 = "Trial 11: Snake trasnformed vs un-trasformed"
graph_11 = untrasform(files_11, my_mean_11, my_sd_11, title1, title2, is_log=FALSE)

title1 = "Trial 12: Newt trasnformed vs un-trasformed"
title2 = "Trial 12: Snake trasnformed vs un-trasformed"
graph_12 = untrasform(files_12, my_mean_12, my_sd_12, title1, title2, is_log=FALSE)

grid.arrange(graph_9[[1]], graph_9[[2]], graph_10[[1]], graph_10[[2]], graph_11[[1]], graph_11[[2]], graph_12[[1]], graph_12[[2]], nrow = 4)
